---
title: "R Notebook"
output: html_notebook
---

# Libraries

```{r}
library(aws.ec2)
library(ssh)
library(remoter)
library(tidyverse)
```


Basic
#https://www.r-bloggers.com/interacting-with-aws-from-r/

Walkthrough
#https://jagg19.github.io/2019/08/aws-r/ (recent and definitive)
#https://jagg19.github.io/2019/08/https-aws-r/ (security angle with load balancer)

ssh from Rstudio desktop and running multicore in parallel
#https://janlauge.github.io/2019/building-our-own-open-source-supercomputer-with-R/

Great series running multiple in parallel
#https://www.daeconomist.com/post/2018-06-27-aws/

Walk through to set up micro instance directly on AWS EC2 with terminal steps
#https://blog.davisvaughan.com/2017/05/15/rstudio-shiny-aws-1/

Cloudyr package
#https://github.com/cloudyr/aws.ec2

Walk through from 2018 sets up only with port 80 and web portal
#http://www.sastibe.de/2018/01/setting-up-a-scalable-rstudio-instance-in-aws/

Win vector has command line code to set up ssh
#http://www.win-vector.com/blog/2018/01/setting-up-rstudio-server-quickly-on-amazon-ec2/
Win vector code to run local + ec2 in parallel
#http://www.win-vector.com/blog/2016/01/running-r-jobs-quickly-on-many-machines/

h20 cluster on h20
#https://redoakstrategic.com/h2oaws/

Discussion of docker ami plus ssh
#https://api.rpubs.com/nathanmietkiewicz/293054

Try to figure out how to run docker with rstudio and python in aws
#https://www.r-bloggers.com/reticulate-virtualenv-and-python-in-linux/

Runs through set up of rocker image to run on aws linux ami
#https://mdneuzerling.com/post/user-getting-started-with-r-and-docker/

Full run through in part 1 setting up linux machine with ssh then install RStudio, then use aws.ec2 package in part 2
#https://www.r-craft.org/category/machine-learning/aws/
#https://www.r-craft.org/r-news/taking-advanced-analytics-to-the-cloud-part-ii-objects-from-s3-to-r-using-the-aws-s3-package/

```{r}
source("https://bit.ly/2KnkdzV")
```


```{r}
Sys.setenv("AWS_ACCESS_KEY_ID" = "AKIAJRFXLSYWKCEEJBMA",
           "AWS_SECRET_ACCESS_KEY" ="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",
           "AWS_DEFAULT_REGION" = "us-east-1")
```


```{r}
# set access credentials
aws_access <- aws.signature::locate_credentials()

```


```{r}

# Describe the AMI (from: http://www.louisaslett.com/RStudio_AMI/)
ami_image <- "ami-0226a8af83fcecb43"
aws_describe <- describe_images(ami_image)
#aws_describe %>% tidy_describe()
aws_describe[[1]]
```



```{r}
s <- describe_subnets()[[1]]
g <- describe_sgroups()[[1]]
```


```{r}
# create an SSH keypair
my_keypair <- create_keypair("aws-ec2")
pem_file <- tempfile(fileext = ".pem")
cat(my_keypair$keyMaterial, file = pem_file)
## delete keypair
#delete_keypair(mykeypair)
```



```{r}
aws_type <- "t2.medium"
#ssh_private_key_file <- "aws-rstudio.pem"

ec2inst <- run_instances(
  image = ami_image,
  type = aws_type,
  sgroup=g,
  subnet=s,
  spot_options = c("MaxPrice" = "0.016"),
  keypair = my_keypair
  )

Sys.sleep(30)
ec2inst <- describe_instances(ec2inst)
ec2inst %>% tidy_describe()

ec2inst_ip <- get_instance_public_ip(ec2inst)

```




```{r}
aws_status <- instance_status(ec2inst)
aws_status %>% tidy_describe()
```



```{r}
instance_ip <- get_instance_public_ip(ec2inst)
if (is.na(instance_ip)) {
    instance_ip <- associate_ip(i, ips[[1L]])$publicIp
}
try(authorize_ingress(g))
try(authorize_egress(g))
```

```{r}
# log in to instance
library("ssh")
session <- ssh::ssh_connect(paste0("ubuntu@", instance_ip), keyfile = pem_file, passwd = "rstudio")
```


```{r}
# write a quick little R script to execute
#cat("'hello world!'\nsprintf('2+2 is %d', 2+2)\n", file = "helloworld.R")

invisible(ssh::scp_upload(session, "./ct_irs_soi_mid/"))

# upload it to instance
invisible(ssh::scp_upload(session, "load_ct_irs_1.R"))

```

```{r}
# execute script on instance
x <- ssh::ssh_exec_wait(session, "Rscript load_ct_irs_1.R")

```


```{r}

# helper function for a random temporary password
random_tmp_password <- generate_password()
# CMD string to start remoter::server on instance
r_cmd_start_remoter <- str_c(
  "sudo Rscript -e ",
  "'remoter::server(",
  "port = 55555, ",
  "password = %pwd, ",
  "showmsg = TRUE)'",
  collapse = "") %>%
  str_replace("%pwd", str_c('"', random_tmp_password, '"'))

# connect and execute
plan(multicore)
x <- future(
  ssh_exec_wait(
    session = con,
    command = r_cmd_start_remoter))

remoter::client(
  addr = ec2ip,
  port = 55555,
  password = random_tmp_password,
  prompt = "remote")


```


```{r}
stop_instances(ec2inst)
terminate_instances(ec2inst)
```